Fast Sorting on Modern Computers

### 2005-08-18 docs/tech_report/conclusions.tex
branch prediction summary for shellsorts

TODO shell

%TODO results from software predictors

>>>>

We are able to accurately predict the number of branch mispredictions in
shellsort, using our results from insertion sort. We also found that the
improvement mode to shellsort, seperating the final loop from the rest, results
in keys being moved 1.07 places, up from 1.03, contributing to its improved
performance.

### 2005-08-18 docs/tech_report/shell.tex
branch prediction summary for shellsorts

%TODO
\section{A More Detailed Look at Branch Prediction}

@@

%TODO see figure something
In shellsort, almost exactly half of the important branches are mispredicted.
Simply predicting that all branches are taken would result in a slightly higher
prediction ratio of 50.8\%. Similarly, for improved shellsort, slightly more
than half of the branches are correctly predicted, at 50.3\%, rising to 53\%
using a strategy of predicting all branches as taken. These results can be seen
in Figures \ref{Branch prediction performance for Shellsorts}.

The results also show that in shellsort, a key moves only 1.03 places down the
array, on average, during each iteration. In improved shellsort, each key moves
over 1.07\% places each iteration, while in the final insertion sort, each key
moves an average of 2.1 places.

The expected number of branch mispredictions is $log_{(\frac{11}{5})}N$.  This
is almost exactly correct, being slightly lower (18.48 mispredictions per key,
instead of 19.34, for 4194304 keys).

>>>>

\section{A More Detailed Look at Branch Prediction}

@@

In shellsort, almost exactly half of the important branches are mispredicted.
Simply predicting that all branches are taken would result in a slightly higher
prediction ratio of 50.8\%. Similarly, for improved shellsort, slightly more
than half of the branches are correctly predicted, at 50.3\%, rising to 53\%
using a strategy of predicting all branches as taken. These results can be seen
in Figures \ref{Branch prediction performance for Shellsorts}.

The results also show that in shellsort, a key moves only 1.03 places down the
array, on average, during each iteration. In improved shellsort, each key moves
over 1.07 places each iteration, while in the final insertion sort, each key
moves an average of 2.1 places.

The expected number of branch mispredictions is $log_{(\frac{11}{5})}N$. This
is almost exactly correct, being slightly lower (18.48 mispredictions per key
instead of 19.34, for 4194304 keys).
